ABC

### 2024-07-10 tabset.qmd
abc

::: {.callout-caution collapse="true"}
## {{< var tabh.h1 >}}
```{r, echo=FALSE, results='asis',warning=F}
apps <- basc
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## {{< var tabh.h2 >}}
```{r, echo=FALSE, results='asis',warning=F}
apps <- basc
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## {{< var tabh.h3 >}}
```{r, echo=FALSE, results='asis',warning=F}
apps <- basc
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## {{< var tabh.h4 >}}
```{r, echo=FALSE, results='asis',warning=F}
apps <- basc
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

>>>>

::: {.callout-caution collapse="true"}
## {{< var tabh.h0 >}}
```{r, echo=FALSE, results='asis',warning=F}
apps <- basc
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## {{< var tabh.h1 >}}
```{r, echo=FALSE, results='asis',warning=F}
apps <- rigv[[1]]
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## {{< var tabh.h2 >}}
```{r, echo=FALSE, results='asis',warning=F}
apps <- rigv[[2]]
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## {{< var tabh.h3 >}}
```{r, echo=FALSE, results='asis',warning=F}
apps <- rigv[[3]]
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::
